---
output: 
  BiocStyle::html_document2:
    toc: true
    toc_float: true
    css: readthedown.css
---


```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```


# My problems with Rmd

So I really would like to use Rmd for documents that mix R with text. But
it is being awfully hard, compared to using Rnw (which mixes good, old,
LaTeX).

Why? Because PDFs are inflexible, and HTML resizing on the fly is great
for many technical documents you read in different devices.


## What is this

Some notes. For me, basically.


## General issues

1. Rendering to both HTML and PDF is not as easy as you might believe, in
particular if you want specific things.  Markdown is supposed to be easy,
but I've spent much more time in three days googling around how to do
things than I spend using LaTeX over extended periods of time.


2. I've found issues with some templates/functions from BioC. In
particular, pdf_document2 crashes with some constructs, and pdf_document
will not accept the `\@ref` syntax.




## Tables really suck in markdown

So building tables in LaTeX used to be a piece of cake, with infinite
configurability. Markdown? Man, it is terribly hard to get what you
want. And you need to carefully play ascii code. And then renderers will
do all sorts of things. 

### Notes and examples of tables here

Great resource:

<https://cran.r-project.org/web/packages/pander/vignettes/pandoc_table.html>


# A simple table from emacs

but it cannot be aligned

+-----+-----+-----+---------------+
|A    |  E  |I    |       O       |
+=====+=====+=====+===============+
|1    |  3  |4    |    1237 8     |
|     |     |     |               |
+-----+-----+-----+---------------+
|2    |  4  |6    |78989080808098 |
+-----+-----+-----+---------------+

### What matters is placement of first {#ref1}

This is my preferred style.

----------------------------------------
A           B               C       D
-------     ------ ----------   -------
     12     12        12             12
	 
    123     123       123           123
	
      1     1          1              1
-------     ------ ----------   -------


### This will not expand to full column, and allows col. justification


---------------------------------------
      A     B          C              D
-------     ------ ----------   -------
     12     12        12             12

    123     123       123           123

      1     1          1              1
----------------------------------------



-------------------------------------------------------------
 Centered   Default           Right Left
  Header    Aligned         Aligned Aligned
----------- ------- --------------- -------------------------
   First    row                12.0 Example of a row that
                                    spans multiple lines.

  Second    row                 5.0 Here's another one. Note
                                    the blank line between
                                    rows.
-------------------------------------------------------------


+-----+-----+-----+-----+
|    A|    E|I    |O    |
+=====+=====+=====+=====+
|    1|    3|4    |8  |
+-----+-----+-----+-----+
|    2|    4|6    |7   |
+-----+-----+-----+-----+







## Another table 


+----------------+-------+-------+--------+------+
|                |  mpg  |  cyl  |  disp  |  hp  |
+================+=======+=======+========+======+
| Mazda RX4      |  21   |   6   |  160   | 110  |
+----------------+-------+-------+--------+------+
| zda RX4 Wag    |  21   |   6   |  160   | 110  |
+----------------+-------+-------+--------+------+
| atsun 710      | 22.8  |   4   |  108   |  93  |
+----------------+-------+-------+--------+------+


## Do you expect these to be aligned where you think?


I cannot understand the formatting. No idea since they look very similar
to Emacs' ones. 

+----------------+---------------+----------------+
|   Sepal.Length |   Sepal.Width |   Petal.Length |
+================+===============+================+
|            5.1 |           3.5 |            1.4 |
+----------------+---------------+----------------+
|            4.9 |             3 |            1.4 |
+----------------+---------------+----------------+



+------------------+-------+-------+--------+------+--------+
|                  | mpg   | cyl   | disp   | hp   | drat   |
+==================+=======+=======+========+======+========+
|        Mazda RX4 | 21    | 6     | 160    | 110  | 3.9    |
+------------------+-------+-------+--------+------+--------+
|    Mazda RX4 Wag | 21    | 6     | 160    | 110  | 3.9    |
+------------------+-------+-------+--------+------+--------+




+-----------------+---------------+----------------+
|   Sepal.Length  |   Sepal.Width |   Petal.Length |
+=================+===============+================+
|            5.1  |           3.5 |            1.4 |
+-----------------+---------------+----------------+
|            4.9  |             3 |            1.4 |
+-----------------+---------------+----------------+


### This was created with emacs table mode

And it does not do anything strange. I just don't get it.

+-----+-----+-----+
|    a|    e|    i|
+=====+=====+=====+
|    9|    8|    7|
+-----+-----+-----+




## A table {#ref0}


This will often span the whole column. Why, oh why!



Fruit   | Price
------- | -----
bananas | 1.2
apples  | 1.0
oranges | 2.5




|Fruit   | Price |
|------- | ----- |
|bananas | 1.2	 |
|apples  | 1.0	 |
|oranges | 2.5	 |




I want to refer to \@ref(ref1)

```{r}
knitr::kable(
  head(mtcars, 10), booktabs = TRUE,
  caption = 'A table of the first 10 rows of the mtcars data.'
)
```


## A nested one

Bloblo

I want to refer to \@ref(ref1)

I want to refer to \@ref(ref0)
